\textbf{CMCS 818J Project Final Report} \\ Implementing Streaming Authenticated Data Structures

### 2012-12-20 doc/final_report/draft_report.tex

	The Streaming Authenticated Data Structure scheme (SADS) \cite{dads} does not require any interaction between the client and the server while the stream is observed.
	Three important properties are obtained using this scheme :
	\begin{enumerate}[a.]
		\item Independence of prover (server) and verifier (client) : the prover and the verifier can update internal state without interaction.
		\item Efficiency : SADS demonstrates an exponential improvement in server's running time for many common query types.
		\item Expressiveness : a wide range of queries such as (non-)membership, successor, range search and frequencies can be supported
	\end{enumerate} 
	The ultimate goal of the proposed scheme is to implement the SADS scheme that enable the verification of computation performed by an untrusted resource.

>>>>

	The Streaming Authenticated Data Structure scheme (SADS) \cite{sads} does not require any interaction between the client and the server while the stream is observed.
	Three important properties are obtained using this scheme :
	\begin{enumerate}[a.]
		\item Independence of prover (server) and verifier (client) : the prover and the verifier can update internal state without interaction.
		\item Efficiency : SADS demonstrates an exponential improvement in server's running time for many common query types.
		\item Expressiveness : a wide range of queries such as (non-)membership, successor, range search and frequencies can be supported
	\end{enumerate}
	The ultimate goal of the proposed scheme is to implement the SADS scheme that enable the verification of computation performed by an untrusted resource.
